Staged Abstract Interpreters

### 2019-09-05 paper/paper.tex
misc

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  We thank the reviewers of PLDI '19 and OOPSLA '19, as well as James Decker,
  Guanhong Tao, Gr\`egory Essertel, and Fei Wang for their feedback on the early
  drafts. We thank David Van Horn and David Darais for their encouragement on
  this work.
  This work was supported in part by NSF awards 1553471, 1564207, 1918483, DOE
  award DE-SC0018050, as well as gifts from Google, Facebook, and VMware.

>>>>

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  We thank the reviewers of PLDI '19 and OOPSLA '19, as well as James Decker,
  Guanhong Tao, Gr\'egory Essertel, and Fei Wang for their feedback on the early
  drafts. We thank David Van Horn and David Darais for their encouragement on
  this work.
  This work was supported in part by NSF awards 1553471, 1564207, 1918483, DOE
  award DE-SC0018050, as well as gifts from Google, Facebook, and VMware.
